### 2018-09-13 doc/results.tex
cut point caption

Our best model, as selected via LOOIC and WAIC, is the parameter rich ``past and vary'' model which includes our historical covariantes and allows all regression parameters to vary through time (Table \ref{tab:selection}). Our best model is an improvement over the next best model by approximately 13 LOOIC and 24 WAIC points. However, the actual differences between these models are minor as revealed by the wide the standard errors. These results mean that while our ``past and vary'' model could be considered the best of the four, all four of the models are very close and only offer incremental improvement but not major differences.
\begin{table}[ht]
  \centering
  \caption{Model comparison using WAIC and LOOIC}
  \begin{tabular}{ r r r r r }
    \hline
    Model & looic & looic se & waic & waic se \\
    \hline
    Past and vary & 12789.81 & 178.90 & 12785.51 & 178.84 \\
    No past but vary & 12820.67 & 178.82 & 12817.49 & 178.77 \\ 
    Past but no vary & 12847.18 & 179.40 & 12844.88 & 179.36 \\ 
    No past or vary & 12851.43 & 179.48 & 12849.10 & 179.44 \\ 
    \hline
  \end{tabular}
  \label{tab:selection}
\end{table}

As described above, our data is extremely unbalanced with respect to the number of extinction events relative to the total number of observations; this reality means that 0.5 is an inappropriate cutpoint for estimating if a species observation is their last (i.e. goes extinct). New, optimal cutpoint were calculated from the ROC curve as the level which maximized the true and false positive rates.
The distributions of optimal cut-off point estimates for each of the four models are broadly similar, with all 50\% credible intervals overlapping.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio=true]{figure/cut_plot}
  \caption{Posterior estimates of the optimal cutpoints for each of the three models. The optimal cutpoint corresponds to the point which maximizes the true and false positive rates.}
  \label{fig:cut_point}
\end{figure}

>>>>

Our best model, as selected via LOOIC and WAIC, is the parameter rich ``past and vary'' model which includes our historical covariantes and allows all regression parameters to vary through time (Table \ref{tab:selection}). Our best model is an improvement over the next best model by approximately 13 LOOIC and 24 WAIC points. However, the actual differences between these models are minor as revealed by the wide the standard errors. These results mean that while our ``past and vary'' model could be considered the best of the four, all four of the models are very close and only offer incremental improvement but not major differences.
\begin{table}[ht]
  \centering
  \caption{Model comparison using WAIC and LOOIC}
  \begin{tabular}{ r r r r r }
    \hline
    Model & looic & looic se & waic & waic se \\
    \hline
    Past and vary & 12784.04 & 178.71 & 12784.04 & 178.71 \\
    No past but vary & 12819.01 & 178.80 & 12819.01 & 178.80 \\ 
    Past but no vary & 12847.00 & 179.38 & 12847.00 & 179.38 \\ 
    No past or vary & 12851.53 & 179.48 & 12851.53 & 179.48 \\ 
    \hline
  \end{tabular}
  \label{tab:selection}
\end{table}

As described above, our data is extremely unbalanced with respect to the number of extinction events relative to the total number of observations; this reality means that 0.5 is an inappropriate cutpoint for estimating if a species observation is their last (i.e. goes extinct). New, optimal cutpoint were calculated from the ROC curve as the level which maximized the true and false positive rates.

The distributions of optimal cut-off point estimates for each of the four models are broadly similar, with all 50\% credible intervals overlapping.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio=true]{figure/cut_plot}
  \caption{Posterior estimates of the optimal cutpoints for each of the three models. The optimal cutpoint corresponds to the point which maximizes the true and false positive rates; this new cutpoint is used instead of 0.5 when estimating if an observation is the last observation of that species (i.e. goes extinct).}
  \label{fig:cut_point}
\end{figure}
